---
title: "FinalProject_Hopkins_Symphony"
author: "Symphony Hopkins"
date: "2022-12-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include = FALSE}
#Importing Data and Necessary Libraries

library(readr)
day <- read_csv("~/Documents/Maryville_University/DSCI_502/day.csv")

library(pscl)

```

```{r, echo = FALSE, include = FALSE}
#Question 13A
lm_result_13a <- lm(cnt ~ season + weathersit + atemp + registered, data= day)

#Question 13B
lm_result_13b <- lm(cnt ~ season + workingday + weathersit + atemp + registered, data= day)

#Question 13C
lm_result_13c <- lm(cnt ~ season + holiday + workingday + weathersit + atemp + hum + windspeed + registered, data= day)
```

**13)	Build the following multiple linear regression models:**

**a) Perform multiple linear regression with cnt as the response and the predictors are: season, weathersit, atemp, and registered.**

```{r, echo = TRUE}
summary(lm_result_13a)
```

**b) Perform multiple linear regression with cnt as the response and the predictors are: season, workingday, weathersit, atemp, and registered.**

```{r, echo = TRUE}
summary(lm_result_13b)
```

**c) Perform multiple linear regression with cnt as the response and the predictors are: season, holiday, workingday, weathersit, atemp, hum, windspeed, and registered.**

```{r, echo = TRUE}
summary(lm_result_13c)
```

**Based on the multiple linear regression model results...**

*Model A's adjusted R squared value is `r summary(lm_result_13a)$adj.r.squared`.

*Model B's adjusted R squared value is `r summary(lm_result_13b)$adj.r.squared`.

*Model C's adjusted R squared value is `r summary(lm_result_13c)$adj.r.squared`.

**From these results, we can conclude that *Model C* is the best model to recommend to management.**

```{r, echo = FALSE, include = FALSE}
#Question 14A
glm_result_14a <- glm(holiday ~ cnt + season + registered, family=binomial, data=day) 

#Question 14B
glm_result_14b <- glm(holiday ~ cnt + season + weathersit + registered, family=binomial, data=day) 

#Question 14C
glm_result_14c <- glm(holiday ~ cnt + season + weathersit + workingday + registered, family=binomial, data=day) 
```

**14)	Build the following logistic models:**

**a)	forecast holiday using cnt, season, and registered.**
```{r, echo = TRUE}
summary(glm_result_14a)
```
**b)	forecast the holiday using cnt, season, weathersit , and registered.**
```{r, echo = TRUE}
summary(glm_result_14b)
```
**c)	forecast the holiday using cnt, season, weathersit , workingday, and registered**
```{r, echo = TRUE}
summary(glm_result_14c)
```

**Based on the logistic regression model results...**

*Model A's McFadden/pseudo R squared value is `r pR2(glm_result_14a)[4]`.

*Model B's McFadden/pseudo R squared value is `r pR2(glm_result_14b)[4]`.

*Model C's McFadden/pseudo R squared value is `r pR2(glm_result_14c)[4]`.

**From these results, I wouldn’t recommend any of these models to the management; however, if I had to choose, it would be *Model C* because it has the highest McFadden/pseudo R squared value.**
